---
title: "Oil Reservoir Data"
author: "Mark and Quynh"
date: "October 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sessionInfo()
```

## Data Source

```{r, message=F, warning=F, code = readLines('../03 Visualizations/summary-subset.R')}
source('../03 Visualizations/summary-subset.R')
```


## Plot 1 - Permeability vs Porosity

When permeability is plotted against porosity on logspace, we see a clear correlation depsite their being a large spread. Porosity is how much pore space is in the rock. Permeability is how easy fluid flows through a rock. Both are desirable properties for getting oil.

```{r, message=F, warning=F, code = readLines('../02 DataWrangling/plot1.R')}
source('../02 DataWrangling/plot1.R')
```


## Plot 2 - Data Points vs State

We can plot how much data was collected in each state. We see that Texas and Louisiana had the most data collected.

```{r, message=F, warning=F, code = readLines('../02 DataWrangling/plot2.R')}
source('../02 DataWrangling/plot2.R')
```



## Plot 3 - Average Porosity and Permeability vs State

We can get the average reservoir properties in the states. We find that Louisiana, Arkansas, and Mississippi have the most desirable reservoir properties.

```{r, message=F, warning=F, code = readLines('../02 DataWrangling/plot3.R')}
source('../02 DataWrangling/plot3.R')
```
